Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-01-25 docs/manuscript/manuscript.tex
Draft repro attempts

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
A total of \textit{$n_{2}$}=102 (46.7\%) of the authors that responded to our survey reported attempting to reproduce a study in the past two years.
This subset of participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions.
Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (42.2\%) and geographic methods and GIScience (35.3\%).
Respondents attempting reproductions were also focused on quantitative (52.0\%) and mixed-methods (46.1\%) approaches. 
Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.

@@

ACCESS MATERIALS - Q12.
The majority of researchers (82/102) that attempted reproductions were able to access at least some of the data used in the original study, but only (27/102) could access all of the original data.

OUTCOME - Q11 AND OUTCOME BY ACCESS Q12
Geographic researchers report being able to recreate some the results they attempt to reproduce, but few researchers report being able to identically recreate all results (20/102).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
A total of \textit{$n_{2}$}=102 (46.7\%) of the authors that responded to our survey reported attempting to reproduce a study in the past two years.
This subset of participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions.
Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (42.2\%) and geographic methods and GIScience (35.3\%).
Respondents attempting reproductions were also focused on quantitative (52.0\%) and mixed-methods (46.1\%) approaches. 
Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.
Approximately half (49\%) of the researchers attempting reproductions reported submitting their findings for publication.

@@

In most instances, researchers reported some ability to access to the research artifacts used in the study they were attempting to reproduce and the ability to recreate at least some of the results of that study.  
The majority of researchers that attempted reproductions (82\%) were able to access at least some of the data used in the original study, but few researchers (27\%) reported access to all of the original data.
Researchers also reported the ability to access at least some information about study procedures (69\%) and its computational environment (60\%), but limited ability to access all procedural (20\%) and computational information (15\%). 
Less than half of researchers (38\%) reported being able to at least partially reproduce all of the results from an original study.
Similarly, nearly all researchers (96\%) reported at least partially reproducing some results, but less than half (38\%) reported being able to at least partially reproduce all results.
Few researchers (20\%) reported the ability to identically reproduce all results.

OUTCOME - Q11 AND OUTCOME BY ACCESS Q12
\begin{itemize}
    \item If geographic researchers had access to at least some of the data and procedures used in the original study they reported the ability to at least partially reproducing some results in all cases. This indirectly supports researcher beliefs that fraud is not prevalent in the discipline.
    \item Access to data and procedures seems to be equally important to being able to at least partially reproduce all results
    \item Having access to all of the data and all of the procedures used in an original study double the probability that a research would be able to at least partially reproduce all results. $P(C|D=A)=66.7\%$ while $P(C|D=\neg A)=27.4\%$. $P(C|P=A)=70.0\%$ while $P(C|P=\neg A)=30.0\%$.
    \item Same story, given at least some access to whatever is not being modulated. $P(C|D=S,A;P=A)=14/20=0.7$ with $P(C|D=S,A;P=S)=13/43=0.30$ compared to $P(C|D=A;P=S,A)=16/23=0.695$ with $P(C|D=S;P=S,A)=11/40=0.275$
    \item Reverse conditional maybe...
\end{itemize}
